\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors

### 2021-10-06 Manuscript/Manuscript.Rmd
update on ms

There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants [@barrett2002; @schiestl2013], which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions. However, most studies that have explored plant reproductive biology (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated [@carvalheiro2014; @baude2016; @munoz2016; @moeller2017; @grossenbacher2017]. Indeed, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive biology traits [@salguero2016, @ruger2018]. As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking [@roddy2021]. At the same time, there is growing interest in the determinants of plant-pollinator interactions via trait-based approaches [@fenster2004] and trait-matching analyses [@bartomeus2016]. However, floral traits have been overlooked beyond highly specialised plant-pollinator systems [@dellinger2020; @roddy2021] and the role of plant reproductive biology remains little explored in plant-pollinator interactions (but see references [@tur2013; @devaux2014]).

  With the recent availability of large trait databases, plant ecological strategies are increasingly being examined [e.g., TRY; @kattge2011 and COMPADRE; @salguero2015], and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; @carmona2021]. However, the main focus has been on vegetative traits such as leaf [@wright2004] or wood [@chave2009] trade-offs with little or no attention given to reproductive biology and floral traits [@evojtko2020], also critical to plant form and function. For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017]. Further, outcrossing levels are positively correlated with flower size [@goodwillie2010]. In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators [@ollerton2011]. Hence, exploring plant life strategies with reproductive biology and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.

  Several studies have identified links between plant traits and plant-pollinator network properties [@lazaro2008; @bartomeus2013; @carvalheiro2014]. Moreover, plant traits can also define species' network roles (e.g., specialists vs generalists). For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016]. This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012]. Despite the increasing knowledge of the relevance of traits on the species network roles, little is known about how plant reproductive and floral traits determine plant species’ network roles at a macroecological scale.

Here, we explore the potential trade-offs among plant floral and reproductive biology traits and how these influence the structure of plant-pollinator networks. First, we identify the major axes of trait variation and trade-offs that determine plant form and function. Second, we investigate how plant species’ position in trait-space influences their interaction patterns with different guilds of floral visitors. Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks.

>>>>

Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their relevance to understand plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021]. In addition, macroecological studies regarding specific reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and as a consequence studies that link reproductive traits to plant-pollinator interactions at large scales are poorly explored [@sargent2008; @rech2016; @salguero2016; @ruger2018]. Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016]. At the same time, there is increasing interest in the understanding of the determinants of plant-pollinator interactions via trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016]. However, reproductive traits have been overlooked beyond highly specialised systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002]. In addition, it is yet unclear how the different reproductive biology traits influence plant-pollinator associations [@tur2013; @devaux2014].

Species can optimize their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can employ. With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are increasingly being examined, and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021]. However, the main focus has been on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits
[@evojtko2020; @roddy2021], also critical to plant life strategies that shape plant interactions with pollinators and ultimately impact plant reproductive success. For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017]. Further, outcrossing levels are positively correlated with flower size [@goodwillie2010]. In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators [@ollerton2011]. However, it is still unknown to what extent these different  reproductive compromises determine plant-pollinator associations.

Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020]. Moreover, plant traits can also define species' network roles (@lazaro2013; @tur2013)(e.g., specialists vs generalists). For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016]. This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012]. Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013]. Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions. Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.

Here, we explore the potential trade-offs among plant floral and reproductive biology traits and how these influence plant-pollinator interactions. First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function. Second, we investigate how plant species’ position in trait-space influences plant-pollinator interactions (presence-absence and visitation rate). Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
